% !TEX TS-program = xelatex
% !BIB TS-program = bibtex
\documentclass[12pt,letterpaper]{article}
\usepackage{style/dsc180reportstyle}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Title and Authors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Differentially Private Query Release for Telemetry Data}

\author{
\textbf{Reva Agrawal} \\
{\tt ragrawal@ucsd.edu}
\and
\textbf{Jordan Lambino} \\
{\tt jlambino@ucsd.edu}
\and
\textbf{Dhruv Patel} \\
{\tt dhp005@ucsd.edu}
\and
\textbf{Yu-Xiang Wang} \\
{\tt yuxiangw@ucsd.edu}
\and
\textbf{Bijan Arbab} \\
{\tt barbab@ucsd.edu}
}

\begin{document}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Abstract and Links
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
Telemetry data from software and hardware systems is vital for product analytics and quality monitoring, but releasing aggregate statistics can expose individuals to re-identification even when identifiers are removed. This work addresses the need for a rigorous, practical approach to sharing telemetry insights while protecting user privacy. We design and implement a differentially private query-release system: we answer a fixed set of aggregate queries over the data by adding calibrated noise to query outputs, after bounding each user's contribution so that privacy guarantees are well defined. We apply two standard mechanisms, the Laplace and the Analytic Gaussian mechanism, to 12 benchmark queries over Intel telemetry, covering battery usage, display and browser statistics, power and sleep metrics, and process rankings. A total privacy budget is allocated across queries and the system is evaluated in terms of the tradeoff between privacy parameters and the utility of released answers. The work provides a rigorous, auditable foundation for privacy-preserving telemetry analytics that can support product and quality teams without requiring access to raw user-level data.
\end{abstract}

\begin{center}
Code: \url{https://github.com/agrawalreva/intel-telemetry-capstone}

Website: \url{https://agrawalreva.github.io/intel-telemetry-capstone/}
\end{center}

\maketoc
\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Main Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Telemetry data collected from software and hardware systems is essential for product analytics, quality monitoring, and performance tuning. Such data is typically user-level or device-level: each record is associated with an identifier (a device GUID), and multiple records can belong to the same identifier. Releasing aggregate statistics over this data enables valuable insights but poses privacy risks; even after removal of direct identifiers, datasets can remain vulnerable to re-identification and linkage attacks. Differential privacy (DP) provides a rigorous framework for releasing query answers by limiting the influence of any single individual on the output. In this work we focus on \emph{query release}: we answer a fixed set of aggregate SQL queries under DP by adding calibrated noise to their results, after bounding each user's contribution via clipping. We implement two standard mechanisms, the Laplace mechanism and the Analytic Gaussian mechanism, on Intel telemetry, with the goal of evaluating the tradeoff between privacy parameters and utility.

\subsection{Motivation}
\label{sec:motivation}

Organizations that collect telemetry at scale require aggregate statistics for collaboration, benchmarking, and research while protecting individual users. Removal of direct identifiers alone does not prevent inference from rich behavioral traces. Query-based release under DP offers a principled alternative: analysts receive noisy answers to predefined queries, with a formal guarantee that the probability of any output event changes by at most a multiplicative factor $e^\epsilon$ (and an additive $\delta$ when applicable) when one user's data is added or removed. Implementing this approach in practice requires (1) defining the unit of privacy (in this work, one GUID), (2) deriving and bounding each query's global sensitivity, (3) selecting a mechanism and calibrating noise to that sensitivity, and (4) accounting for composition when multiple queries are answered. This work addresses these requirements in the context of a large telemetry corpus and a fixed set of 12 analytical queries.

\subsection{Differential Privacy}
\label{sec:dp_definitions}

\paragraph{Neighboring datasets.}
We consider datasets that differ in the records of a single user. Formally, two datasets $D$ and $D'$ are \emph{neighboring} (user-level) if one can be obtained from the other by adding or removing all records belonging to one GUID. Thus, the presence or absence of one user's entire activity is the protected change.

\paragraph{Definition of $(\epsilon,\delta)$-differential privacy.}
A randomized mechanism $\mathcal{M}$ with range $\mathcal{R}$ satisfies $(\epsilon,\delta)$-differential privacy if for all pairs of neighboring datasets $D$, $D'$ and for all measurable sets $S \subseteq \mathcal{R}$,
\begin{equation}
\label{eq:dpdef}
\Pr[\mathcal{M}(D) \in S] \leq e^{\epsilon} \, \Pr[\mathcal{M}(D') \in S] + \delta.
\end{equation}
When $\delta = 0$, the mechanism satisfies pure $\epsilon$-differential privacy ($\epsilon$-DP). Smaller $\epsilon$ and $\delta$ imply stronger privacy.

\paragraph{Global sensitivity.}
Let $f$ be a real-valued function over datasets. The \emph{global sensitivity} of $f$ is
\begin{equation}
\Delta f = \max_{D \sim D'} |f(D) - f(D')|,
\end{equation}
where the maximum is over all neighboring pairs $D$, $D'$. The sensitivity is a worst-case bound and must not depend on the data. We use the following rules:
\begin{itemize}
    \item \textbf{Count query:} $\Delta f = 1$ (adding/removing one GUID changes the count by at most 1).
    \item \textbf{Sum query with per-GUID clipping bound $C$:} $\Delta f = C$ (one GUID can contribute at most $C$ to the sum after clipping).
    \item \textbf{Average query:} If the average is over at least $k_{\min}$ GUIDs and each GUID's contribution is clipped to $C$, then $\Delta f = C / k_{\min}$.
    \item \textbf{Histogram bin:} Each bin is a count; $\Delta f = 1$ per bin. For a vector of $d$ bins, if each GUID contributes to at most one bin, the $\ell_1$ sensitivity of the vector is $1$ and the $\ell_2$ sensitivity is $1$.
\end{itemize}

\paragraph{Laplace mechanism.}
For a function $f$ with $\ell_1$ global sensitivity $\Delta_1 f$, the Laplace mechanism releases
\begin{equation}
\mathcal{M}(D) = f(D) + \text{Lap}(0, b), \quad b = \frac{\Delta_1 f}{\epsilon}.
\end{equation}
This mechanism satisfies pure $\epsilon$-DP \cite{dwork2014promise}. For vector-valued $f$, independent Laplace noise with scale $b$ is added to each coordinate (sensitivity is the $\ell_1$ norm of the per-coordinate sensitivities).

\paragraph{Analytic Gaussian mechanism.}
For $(\epsilon,\delta)$-DP, the Gaussian mechanism adds $\mathcal{N}(0, \sigma^2)$ noise. The classical calibration uses $\sigma \geq (\Delta_2 f / \epsilon) \sqrt{2 \ln(1.25/\delta)}$, where $\Delta_2 f$ is the $\ell_2$ global sensitivity. The \emph{Analytic Gaussian mechanism} \cite{balle2018improving} calibrates $\sigma$ via the Gaussian CDF to obtain a tighter (smaller) noise scale for the same $(\epsilon,\delta)$, improving utility especially in high- and low-privacy regimes. We use either the classical or the analytic calibration; in both cases $\Delta_2 f$ is the Euclidean norm of the per-output sensitivity vector.

\paragraph{Composition.}
If mechanism $\mathcal{M}_1$ is $(\epsilon_1,\delta_1)$-DP and $\mathcal{M}_2$ is $(\epsilon_2,\delta_2)$-DP, their sequential composition yields $(\epsilon_1+\epsilon_2,\, \delta_1+\delta_2)$-DP (basic composition). Advanced composition theorems allow a smaller total $\epsilon$ in exchange for a larger $\delta$. In our system we allocate a total privacy budget $\epsilon_{\text{total}}$ across the 12 queries and state the composed guarantee $(\sum_i \epsilon_i, \sum_i \delta_i)$-DP explicitly (Section~\ref{sec:budget}).

\paragraph{Post-processing.}
If $\mathcal{M}$ is $(\epsilon,\delta)$-DP and $g$ is any deterministic function, then $g \circ \mathcal{M}$ is $(\epsilon,\delta)$-DP. Clamping negative counts to zero or re-normalising percentages after adding noise is deterministic and therefore does not weaken the guarantee.

\paragraph{Report Noisy Max.}
For queries that select the maximum over a set of candidates (for example, the winner per group), we use Report Noisy Max: add independent Laplace noise to each candidate value and return the index of the maximum noisy value. The privacy cost is one $\epsilon$ for the entire selection \cite{dwork2014promise}.

\subsection{Telemetry Data}
\label{sec:telemetry_data}

The data used in this work is Intel telemetry accessed through Globus. The source data consists of 23 tables across two schemas: \textbf{university\_analysis\_pad} and \textbf{university\_prod}. Each row is associated with a device identifier (GUID); multiple rows per GUID are common. The data exhibits heavy-tailed distributions; hence a small fraction of GUIDs can contribute disproportionately to aggregates. We therefore \emph{clip} per-GUID contributions before aggregation so that global sensitivity is bounded by a fixed constant. Concretely, we cap quantities (including the number of power-on events per GUID and the total duration per GUID in a given category) at constants $C_1$, $C_2$, and similar bounds, as specified per query in Section~\ref{sec:methods}. The aggregate query is then evaluated on the clipped view and the DP mechanism is applied to the query output. Clipping is a deterministic pre-processing step; global sensitivity is computed with respect to the clipped query function only.

We use a specialized reporting layer of 22 pre-aggregated tables built from the raw tables via a SQL build script, and we run 12 benchmark queries covering battery usage by geography and CPU family, display device vendor market share, browser popularity by country, OS-level MODS blockers, RAM utilization, persona-level web category usage, and process power rankings. The 12 query results are exported as baseline (non-private) CSVs. We then apply, per query, either the Laplace or the Analytic Gaussian mechanism (Section~\ref{sec:global_model}), with epsilon allocated via sequential composition (Section~\ref{sec:budget}). Post-processing consists of clamping numeric outputs to non-negative values where required and re-normalising percentage columns to sum to 100\% where applicable. The pipeline is developed and validated on a subsample database (approximately 5\,GB) before execution on the full dataset (approximately 3.6\,TB).

\subsection{Applications}
\label{sec:applications}

Privacy-preserving query release over telemetry supports usage metrics and feature adoption by segment, performance and health monitoring by geography or hardware family, market share and ranking statistics, and anomaly detection (identification of segments with unusually high error rates or power draw). Analysts receive noisy answers suitable for trend analysis and prioritisation without access to raw user-level data. The same framework applies to other telemetry or event-log datasets where user-level differential privacy is required.

\subsection{Related Work}
\label{sec:related}

Differential privacy was introduced in \cite{dwork2006calibrating} and is treated in depth in \cite{dwork2014promise}, which covers the Laplace and Gaussian mechanisms, global sensitivity, and composition. The Analytic Gaussian mechanism of \cite{balle2018improving} improves noise calibration for $(\epsilon,\delta)$-DP and is well suited to query release when many numeric outputs are perturbed. Query answering under DP in database and analytics settings requires bounding sensitivity (typically via clipping or projection) and allocating privacy budget across queries. In this work we do not use data-dependent sensitivity, $N$-factor scaling, or averaging over multiple draws to reduce noise; all guarantees follow from standard mechanisms and explicit sequential composition.

\section{Methods}

\subsection{Data Access and Reporting Layer}
\label{sec:data_access}

Raw Intel telemetry is stored in 23 tables across \texttt{university\_analysis\_pad} and \texttt{university\_prod}. We build two DuckDB databases: a subsample with each table capped at 200\,MB for development, and a full database for production. A SQL build script constructs 22 reporting tables (including \texttt{reporting.system\_batt\_dc\_events}, \texttt{reporting.system\_sysinfo\_unique\_normalized}, \texttt{reporting.system\_display\_devices}, and \texttt{reporting.system\_web\_cat\_usage}) that resolve joins and normalize column names. The 12 benchmark queries are executed against this reporting layer; their results are exported to CSV and serve as the non-private baseline. Per-query clipping is applied either in SQL or in the sensitivity analysis. All sensitivity bounds are data-independent and depend only on the clipping constants and query structure.

\subsection{Global Privacy Model}
\label{sec:global_model}

\textbf{Unit of privacy.} We use \emph{user-level} differential privacy: the unit of privacy is one GUID. Neighboring datasets $D$ and $D'$ differ in all rows associated with exactly one GUID (i.e., adding or removing one user's entire activity).

\textbf{Contribution bounding.} Before aggregation we apply per-GUID contribution clipping so that the influence of any single GUID on the query output is bounded. Clipping is a deterministic, data-independent pre-processing step; global sensitivity is computed with respect to the clipped query function.

\textbf{Sensitivity.} For each query we derive the global sensitivity $\Delta f$ (or $\Delta_1 f$, $\Delta_2 f$ for vector outputs) from the clipping bounds and the query structure. We do not use data-dependent sensitivity.

\textbf{Mechanisms.} We apply one of two mechanisms to the query output:
\begin{itemize}
    \item \textbf{Laplace mechanism} (pure $\epsilon$-DP): release $f(D) + \text{Lap}(0, b)$ with $b = \Delta_1 f / \epsilon$. We use Laplace for count queries, histograms, Report Noisy Max (argmax), and low-dimensional grouped aggregates.
    \item \textbf{Analytic Gaussian mechanism} ($(\epsilon,\delta)$-DP): release $f(D) + \mathcal{N}(0, \sigma^2)$ where $\sigma$ is calibrated using the Analytic Gaussian mechanism \cite{balle2018improving}. We assign the Analytic Gaussian mechanism to high-dimensional vector outputs (Query 8), multi-metric grouped releases (Query 7), and average queries (Query 9), and the Laplace mechanism to all other queries (Queries 1 to 6 and 10 to 12; see Section~\ref{sec:methods}). For the Gaussian mechanism we fix $\delta = 10^{-6}$ per query.
\end{itemize}

\textbf{Composition.} The 12 queries are answered under \emph{sequential composition}: if query $i$ uses $(\epsilon_i, \delta_i)$-DP, the total guarantee is $(\sum_{i=1}^{12} \epsilon_i,\, \sum_{i=1}^{12} \delta_i)$-DP. We allocate a total budget $\epsilon_{\text{total}}$ so that $\sum_{i=1}^{12} \epsilon_i \leq \epsilon_{\text{total}}$. When a single query releases multiple numeric outputs, we either split that query's $\epsilon_i$ across outputs or treat the output as a vector and apply the vector-valued mechanism once; we do not treat columns as independent without accounting for composition.

\textbf{Post-processing.} Deterministic post-processing (clamping to non-negative, re-normalising percentages to sum to 100\%) does not consume privacy budget and preserves $(\epsilon,\delta)$-DP.

\subsection{Query 1: Battery Power On Geographic Summary}
\label{sec:q1}

\textbf{Source tables:} \texttt{reporting.system\_batt\_dc\_events} (guid, num\_power\_ons, duration\_mins), \texttt{reporting.system\_sysinfo\_unique\_normalized} (guid, countryname\_normalized).

\textbf{Mathematical definition.} Group by country. For each country $c$: $f_c^{\text{sum}}(D) = (\text{Sum}(\text{num\_power\_ons}), \text{Sum}(\text{duration\_mins}))$ after clipping; $f_c^{\text{count}}(D) = \text{Count}(\text{GUIDs})$. We release sums and count, or averages as noisy sum / max(noisy count, $k_{\min}$).

\textbf{Contribution bounding.} For each GUID: clip total \texttt{num\_power\_ons} to $C_1 = 10$ and total \texttt{duration\_mins} to $C_2 = 60$. Averages use $k_{\min} = 100$ so $\Delta_{\text{avg}} = C/k_{\min}$.

\textbf{Sensitivity.} Per country: $\Delta \,\text{Sum}(\text{num\_power\_ons}) = C_1$, $\Delta \,\text{Sum}(\text{duration\_mins}) = C_2$, $\Delta \,\text{Count} = 1$. Each GUID in one country (parallel composition across countries). L1 $= C_1 + C_2 + 1$; L2 $= \sqrt{C_1^2 + C_2^2 + 1}$.

\textbf{Mechanism:} Laplace (low-dimensional grouped aggregate). Epsilon: $\epsilon_1$ (medium).

\textbf{Post-processing:} Clamp counts and sums $\geq 0$; averages from noisy sum/count with floor.

\subsection{Query 2: Battery On Duration by CPU Family and Generation}
\label{sec:q2}

\textbf{Source tables:} \texttt{reporting.system\_cpu\_metadata} (guid, marketcodename, cpugen), \texttt{reporting.system\_batt\_dc\_events} (guid, duration\_mins).

\textbf{Mathematical definition.} Group by (marketcodename, cpugen). $f_g(D) = \text{Sum}(\text{duration\_mins})$ and count, after per-GUID clipping.

\textbf{Contribution bounding.} Clip each GUID's total \texttt{duration\_mins} to $C = 60$.

\textbf{Sensitivity.} $\Delta \,\text{Sum} = C$, $\Delta \,\text{Count} = 1$. L1 $= C + 1$; L2 $= \sqrt{C^2 + 1}$.

\textbf{Mechanism:} Laplace. Epsilon: $\epsilon_2$ (medium). \textbf{Post-processing:} Clamp $\geq 0$.

\subsection{Query 3: Display Devices Connection Type Resolution Durations AC/DC}
\label{sec:q3}

\textbf{Source tables:} \texttt{reporting.system\_display\_devices} (guid, connection\_type, resolution\_height, resolution\_width, duration\_ac, duration\_dc).

\textbf{Mathematical definition.} Group by (connection\_type, resolution\_height, resolution\_width). Per group: $\text{Sum}(\text{duration\_ac})$, $\text{Sum}(\text{duration\_dc})$, count.

\textbf{Contribution bounding.} Clip per-GUID \texttt{duration\_ac} and \texttt{duration\_dc} to $C_{\text{ac}} = C_{\text{dc}} = 3600$ seconds.

\textbf{Sensitivity.} $\Delta \,\text{Sum}(\text{duration\_ac}) = C_{\text{ac}}$, $\Delta \,\text{Sum}(\text{duration\_dc}) = C_{\text{dc}}$, $\Delta \,\text{Count} = 1$. L1 $= C_{\text{ac}} + C_{\text{dc}} + 1$. One vector per group; charge $\epsilon_3$ once for full query.

\textbf{Mechanism:} Laplace. Epsilon: $\epsilon_3$ (smaller). \textbf{Post-processing:} Clamp $\geq 0$.

\subsection{Query 4: Display Devices Vendors Percentage}
\label{sec:q4}

\textbf{Source tables:} \texttt{reporting.system\_display\_devices} (guid, vendor\_name).

\textbf{Mathematical definition.} Count per vendor; total count. Percentage = (count / total)$\times 100$. Each GUID contributes at most 1 to one vendor.

\textbf{Contribution bounding.} Each GUID contributes at most 1 to one vendor bin. $\Delta = 1$ per bin; total count $\Delta = 1$. We release noisy (count per vendor, total); percentages computed after noise (post-processing).

\textbf{Mechanism:} Laplace (histogram). Epsilon: $\epsilon_4$ (smaller).

\textbf{Post-processing:} Clamp counts $\geq 0$; compute percentages from noisy counts; re-normalise to sum to 100\%.

\subsection{Query 5: MODS Blockers by OS Name and Codename}
\label{sec:q5}

\textbf{Source tables:} \texttt{reporting.system\_mods\_top\_blocker\_hist} (guid, dt), \texttt{reporting.system\_os\_codename\_history} (guid, min\_ts, max\_ts, os\_name, os\_codename). Join on GUID and time windows.

\textbf{Mathematical definition.} Count per (os\_name, os\_codename). Each GUID bounded to contribute at most 1 per bin (distinct-GUID count) or cap total entries per GUID at $C_{\text{entries}}$.

\textbf{Contribution bounding.} We use $\Delta = 1$ per bin for distinct-GUID counts. For $B$ bins: vector L1 $\leq B$, L2 $\leq \sqrt{B}$.

\textbf{Mechanism:} Laplace (histogram). Epsilon: $\epsilon_5$ (smaller). \textbf{Post-processing:} Clamp $\geq 0$.

\subsection{Query 6: Most Popular Browser in Each Country by System Count}
\label{sec:q6}

\textbf{Source tables:} \texttt{reporting.system\_sysinfo\_unique\_normalized} (guid, countryname\_normalized), \texttt{reporting.system\_web\_cat\_usage} (guid, browser).

\textbf{Mathematical definition.} Per country: release $\arg\max_{\text{browser}} \text{Count}(\text{GUIDs})$. Each GUID contributes 1 to one (country, browser) cell; $\Delta = 1$ per count.

\textbf{Mechanism:} \textbf{Report Noisy Max.} Per country: add Laplace(0, $1/\epsilon_6$) to each browser count; select argmax. We allocate a single $\epsilon_6$ for the entire query (moderate); composition across countries is accounted for.

\textbf{Post-processing:} None beyond argmax.

\subsection{Query 7: On/Off MODS Sleep Summary by CPU Market Codename and Generation}
\label{sec:q7}

\textbf{Source tables:} \texttt{reporting.system\_on\_off\_suspend\_time\_day} (guid, on\_time, off\_time, mods\_time, sleep\_time), \texttt{reporting.system\_cpu\_metadata} (guid, marketcodename, cpugen).

\textbf{Mathematical definition.} Group by (marketcodename, cpugen). Per group: $\text{Sum}(\text{on\_time})$, $\text{Sum}(\text{off\_time})$, $\text{Sum}(\text{mods\_time})$, $\text{Sum}(\text{sleep\_time})$, count. Averages or percentages derived from these.

\textbf{Contribution bounding.} Clip per-GUID total time per category to $C_{\text{on}}, C_{\text{off}}, C_{\text{mods}}, C_{\text{sleep}}$ (in our implementation, 1440 minutes per day per category). $\Delta \,\text{Sum} =$ the respective $C$ for each time column; $\Delta \,\text{Count} = 1$. L1 $= C_{\text{on}} + C_{\text{off}} + C_{\text{mods}} + C_{\text{sleep}} + 1$.

\textbf{Mechanism:} Analytic Gaussian (multi-metric grouped release). Epsilon: $\epsilon_7$ (medium). Composition: one vector release per group; total $\epsilon_7$ for this query.

\textbf{Post-processing:} Clamp $\geq 0$; re-normalise percentages if computed.

\subsection{Query 8: Persona Web Category Usage Analysis}
\label{sec:q8}

\textbf{Source tables:} \texttt{reporting.system\_sysinfo\_unique\_normalized} (guid, persona), \texttt{reporting.system\_web\_cat\_pivot\_duration} (guid, $\sim$30 web category duration columns).

\textbf{Mathematical definition.} Per persona: number\_of\_systems, days, and $\sim$30 category duration columns (sums or averages). Output is a high-dimensional vector. We treat the entire persona-category vector as a \emph{single} vector-valued query.

\textbf{Contribution bounding.} Clip per-GUID per-category contribution to $C$; then $\Delta \,\text{Sum}_j = C$ per category $j$. The L1 sensitivity of the full vector is $\sum_j \Delta_j$ (in our case $30C$ for 30 category columns). For averages we use $\Delta_{\text{avg}} = C/k_{\min}$ per column. We do \emph{not} treat each column as an independent release; one mechanism call for the full vector.

\textbf{Mechanism:} Analytic Gaussian (high-dimensional vector). Epsilon: $\epsilon_8$ (larger; $\approx 20\%$ of $\epsilon_{\text{total}}$). $\sigma$ calibrated to L2 sensitivity of the vector.

\textbf{Post-processing:} Clamp $\geq 0$; re-normalise distribution columns to sum to 1 or 100\%.

\subsection{Query 9: Package Power by Country}
\label{sec:q9}

\textbf{Source tables:} \texttt{reporting.system\_sysinfo\_unique\_normalized} (guid, countryname\_normalized), \texttt{reporting.system\_hw\_pkg\_power} (guid, nrs, mean).

\textbf{Mathematical definition.} Group by country. Per country: sum of (clipped) mean power, count. Average = sum / max(count, $k_{\min}$). Clip per-GUID mean to $C = 50$ watts; $k_{\min} = 100$. $\Delta \,\text{Sum} = C$, $\Delta \,\text{Count} = 1$; $\Delta_{\text{avg}} = C/k_{\min}$.

\textbf{Mechanism:} Analytic Gaussian (average query). Epsilon: $\epsilon_9$ (medium). \textbf{Post-processing:} Clamp $\geq 0$.

\subsection{Query 10: Popular Browsers by Count Usage Percentage}
\label{sec:q10}

\textbf{Source tables:} \texttt{reporting.system\_web\_cat\_usage} (guid, browser, duration\_ms).

\textbf{Mathematical definition.} Per browser: count of GUIDs, total duration (clipped). Percentages computed in post-processing from noisy counts and sums. Clip per-GUID duration to $C$. $\Delta \,\text{Count} = 1$, $\Delta \,\text{Sum}(\text{duration}) = C$ per browser.

\textbf{Mechanism:} Laplace (count and sum). Epsilon: $\epsilon_{10}$ (smaller).

\textbf{Post-processing:} Clamp counts and sums $\geq 0$; compute percentages; re-normalise to sum to 100\%.

\subsection{Query 11: RAM Utilization Histogram}
\label{sec:q11}

\textbf{Source tables:} \texttt{reporting.system\_memory\_utilization} (guid, sysinfo\_ram, nrs, avg\_percentage\_used).

\textbf{Mathematical definition.} Histogram bins are defined over the RAM dimension (in our schema, \texttt{ram\_gb}). Each GUID contributes to exactly one bin. Per bin we release the count and optionally the average of \texttt{avg\_percentage\_used}. Adding or removing one GUID changes exactly one bin's count by 1. Hence the \textbf{L1 sensitivity of the full histogram vector is 1}.

\textbf{Mechanism:} Laplace (histogram). Epsilon: $\epsilon_{11}$ (smaller). \textbf{Post-processing:} Clamp $\geq 0$; optionally re-normalise.

\subsection{Query 12: Ranked Process Classifications}
\label{sec:q12}

\textbf{Source tables:} \texttt{reporting.system\_mods\_power\_consumption} (user\_id, total\_power\_consumption).

\textbf{Mathematical definition.} $\text{Sum}(\text{total\_power\_consumption})$ per process, with per-user clipping at $C = 100$. Ranking = order of noisy sums (post-processing). Optionally release only top process via Report Noisy Max.

\textbf{Sensitivity.} $\Delta \,\text{Sum} = C$ per process. Full vector L1 = $C \times \text{(\# groups)}$ if one GUID affects one group.

\textbf{Mechanism:} Laplace (sum query; ranking from noisy values). For top-only: Report Noisy Max. Epsilon: $\epsilon_{12}$ (moderate).

\textbf{Post-processing:} Clamp $\geq 0$. Ranking is deterministic post-processing of noisy outputs.

\subsection{Privacy Budget Allocation}
\label{sec:budget}

We fix a total privacy budget $\epsilon_{\text{total}}$ and allocate per-query budgets $\epsilon_1, \ldots, \epsilon_{12}$ such that $\sum_{i=1}^{12} \epsilon_i \leq \epsilon_{\text{total}}$. Allocation policy: Query 8 (high-dimensional) receives approximately 20\% of $\epsilon_{\text{total}}$; core usage queries Q1, Q2, Q7, Q9 receive a medium allocation (approximately 8 to 10\% each); simple histograms and counts (Q4, Q5, Q10, Q11) receive a smaller allocation (approximately 4 to 5\% each); ranking and winner queries (Q6, Q12) receive a moderate allocation (approximately 6 to 8\% each); Q3 receives a smaller allocation. For the Analytic Gaussian mechanism we fix $\delta = 10^{-6}$ per query. Under sequential composition the full system satisfies $(\epsilon_{\text{total}}, \delta_{\text{total}})$-DP with $\epsilon_{\text{total}} = \sum_{i=1}^{12} \epsilon_i$ and $\delta_{\text{total}} = \sum_{i=1}^{12} \delta_i = 12 \times 10^{-6}$.


\end{document}
